%%This is a very basic article template.
%%There is just one section and two subsections.

\documentclass[a4paper,20pt,openany]{article}

\usepackage{apacite}
\usepackage{url}

\title{Reflection Paper on the Group Project}
\date{\today}
\author{Zonglin Li}


\begin{document}
\bibliographystyle{apacite}
\maketitle


\section{My Role in Project}

As group member with relatively more experience about the Chinese restaurant
around campus, I picked the one of the Chinese restaurants (Cravings) as one of
the events on campus we attended. Also, together with Louis, I helped to decide
which Chinese dish we are going to make, and prepared the food with other group
members. Finally, for the presentation, I'm responsible to make the 8th and 9th
slides in the presentation and presented the content of 8th to 11th slides
during the presentation.

\section{Chinese American's identity}

To analysis the way Chinese Americans preserve their ethnic identity, we need to
discuss about the two of the four factors that can influence the salience of
one's identity\cite{book:textbook}. 

\subsection{Perseverance of ethnic identity}

\subsubsection{Culture}
Culture includes lots of aspects, like language, tradition, food, values, family
forms\cite{book:textbook}. For most of the first and second generation Chinese
American, they have Chinese name together with English name. Also, there a huge
number of Chinese speakers around America\cite{misc:languagespeaking}, which
will be good for Chinese American to build connection to their culture. Also,
the Chinese value of family has a strong influence of Chinese American. In
Chinese culture, family is considered as the backbone of the
society\cite{misc:cultureprofile}, which can help the perseverance of ethnic
identity.

\subsubsection{Categorization}
Chinese American, similar to other Asian Americans, are categorized as hard
working, self-control model minorities. Such a categorization can also lead
Chinese American to admit their ethnic identity, especially when they are doing
well in things as school work.

\subsection{Integration to American Culture}
Chinese American immigrants, after they came to American, had made their ways to
integrate to American Culture. They picked their English name, transformed their
business to meet American's requirements. For example, in some Chinese
restaurant, they will prepare dishes specially for American.

\section{The Activities we went on campus}
Since our focus is on the evolution of Chinese food in American, we decided
to compare the food offered in Panda Express, which is considered as the
Americanized Chinese food, and Cravings, which is considered as the
relatively traditional Chinese food. 
We also went to the Asian grocery store near campus, to see the difference
between the things offered there and in other department stores like Walmart.

\section{Some Challenges We faced}
The biggest challenge is to coordinate the time between each group members.
Since we need to attend almost of all our activities during the midterm time,
it's kind of difficult to get a time can satisfy every one. But fortunately, we
finally got a time to go the restaurant together, and to cook the meal.

\bibliographystyle{apacite}
\bibliography{mybib}

\end{document}
