Interview Questions:
\begin{itemize}
  \item Have your parents ever asked you to work for them in the store?
  \item IF yes, THEN Are you willing to work in the store, ELSE Why your parents
  didn't ask you to work for them?
  \item Have your parents ever put a lot of stress on you by continuing telling
  you that how hard they made to immigrant, and how many hope they had on you?
  \item IF yes THEN Have you ever tried to passively response to those pressure
  your parents put on you?
  \item Have you ever done any kinds of cultural brokering for your parents,
  are you the translator of your parents? What do you think the effect of brokering has on you?
  \item How did your parents showed their love to you? Did they speak out
  directly, or by actions like try their best to give you the best financial support, 
  such as avoid buying things for themselves, save all the money for you?
  \item Have you felt a strong feeling to give back your parents?
  \item When you're making decisions, have you tried to consider your
  parents' desire?
  \item Have you ever seen your parents been stressed out, such as they got very
  bad-tempered and unpredictable?
  \item IF yes THEN Had they passed that feeling to you? AND Have your parents
  tried to seek for help from some mental health services? ELSE Turn to the
  parents, and ask them whether they had stressed out before.
  \item Have you heard of a term called ``anjong''\cite[p.~41]{book:ISelected}? 
  \item IF yes THEN what do you think anjong means to your family? Do you think
  being self-employed is a short cut to anjong? ELSE Explain what anjong means
  and ask the same question as ``yes''.
\end{itemize}
