Now, combining the content of the book I chose, and the response from the familyI interviewed, I can do some critical analysis of the influence ofself-employment on children caring.\parFirst, self-employment can really take away the time which supposed to spendwith children from parents. However, this is not necessary mean to be bad forchildren. Granted, it could give a window to some kids with terribleself-control to attempt society disapproved behavior or cause children got badschool performance. The absence of parental control can directly count for that.However, things doesn't always go as it looks. Whether a child can successhighly depends on his or her self-control ability \cite{article:SelfControl}.So, for those ``good kids'' who have a strong self-control, whether or not theirparents are around doesn't affect their performances at school, but for thosewith weak self-control, even though their parents are looking at them 24 hours,they still can develop bad behavior.\parSecond, the involvement of children to parents business can have both good andbad effects, in my opinion. The good thing is that it's an window opened forchildren to interact with society, especially those older than them. Since theycan accumulate the experience of interacting with society when young, when theygrow up, it will be easy for them to adjust. However, helping parents can causebarriers between friends of similar age, because they spend their spare time intheir parents' stores or restaurants. \parFrom the view of contemporary American Society, self-employment really helpedthe new Korean immigrants to overcome the difficulties when adjusting to atotally new environment. For those without good English skills, there is no waymore effective than self-employment to help them settle down in America.However, for those second generations and third generations, they have goodEnglish, their education achievement are accepted by American companies. So,much less of them choose self-employment than their first generation ancestries\cite{online:SecondGenerationSelfEmployment}.