As a specific group of Asian Americans, Korean Americans have most of thecharacteristics of Asian Americans \cite{online:AsianAmericanChar}. They arerespective to the ancestors and elderly, they value the collective interest of awhole family, and they emphasis the importance of be obedience to parents totheir children. However, one thing that makes Korean American stands out istheir high self-employment rate. According to the book I selected, KoreanAmerican has the highest self-employmentrate \cite[p.~14]{book:ISelected}. \parSelf-employment can have a lot of impact on children caring, as stated in theabstract. First, I want to discuss about the impact on the way parents spendtheir time. For self-employed parents, their working time is not fixed. Theymight work late to morning one day, and finish work in the early afternoonanother day. As a result of that flexibility and uncertanty, parents generallywill not try to do much of the children caring works. Most of the childrencaring work and house work will relay either on grandparents or elder children.As described in the book I read, elder children need to take care of the youngerones and do houseworks \cite[p.~22]{book:ISelected}, and as a result, thechildren will have less opportunity to communicate with their parents. Anotherimpact is that the parents will ask their children to help them in theirbussiness in various ways. For example, childrenwill help their parents tending cash registers, docleaning in the restaurant owned by their parents \cite[p.~25]{book:ISelected}.Generally, those helping will happen after school, during which the children aremore willing to play out with their friends. Helping their parents in grocery orrestaurant may cause some barieers for children to maintain their friendshipwith classmates, but is also an opportunity for them to interact and makefriends with adults, who are the clients of their parents' bussiness. Theactually influence will vary from person to person.\parIn my project, I will focus on how the self-employment of parents influencestheir children. In particular, the influence on the relationship betweenchildren and their classmates, between children and their parents, and betweensiblings. I will collect data by interviewing a second generation KoreanAmerican and her family who lives in Chicago whose parents owned a smallgrocery store when she was young.The detail of the interview will be elaborated in section 3.