I chose the book \emph{Caring Across Generations: The Linked Lives of KoreanAmerican Families} as the reading of my project. As its title says, it aboutcaring between family members, but mainly focused on the caring betweengenerations. The population of that book is the Korean immigrants to American,mostly consists of one to third generation of immigrants. Since the firstgeneration immigrants Korean parents are generally not good at English, theyrelay their children who usually have better English skills as the interface tointeract with outside world. Further more, the education of the parents got fromSouth Korea is not usually admitted by the companies in the U.S., so they arefacing downward mobility, which will add financial and spiritual pressure to thefamily. When the children are old enough, they will work in some part-time jobs,or help in their parents' business in order to give their family some support.As parents getting older, and children growing up, children have even moreobligation to take care of their parents, according to the cultural tradition.\parSo, in that book, the authors are focusing on how and by which extend thedifficulties those immigrant parents facing can change the direction ofcaring, and how that changing can influence their relationship with theirchildren. Since Korean American has a significantly high rate ofself-employment, there is no way for the authors of the book to omit the effectof self-employment.\parThe biggest help of that book for my project is giving me a way as asemi-outsider(The reason is that I am not Korean American, but I am AsianAmerican) to peel into the Korean culture and life and make linkages to my ownexperience, and eventually aid my understanding of Korean American. Anotherusage of that book is to prepare my interview questions. The book gave me a lotof ideas of what my interview questions will be, and provided me some backgroundknowledge. For example, the yes branch of the second question, the thirdquestion, the fifth question, the eighth and ninth questions are all createdafter reading the cases of the sample Korean Americans of that book. And myknowledge of the term ``anjong'' for the last two questions comes directly fromthat book \cite[p.~40, p.~41]{book:ISelected}, which means ``establishment,stability, or security,''